Higher-Order unification for free!

### 2024-04-15 paper/main.tex
minor

\noindent
The resolution of $\hoUnifPb_1$ assigns $\lambda x.\lambda y.x$ to $A$
that in turn triggers $\linkStore_3$ and then $\linkStore_4$ by \progressetaleft,
one per $\lambda$ in the solution of $A$.
The unification variable $C_{yx}$ is therefore unified with $x$
(the second variable of its scope).
As a result $\linkStore_1$ becomes \linketaM{x}{E_x}{\lambda y.y},
and the \rhs is no more in \maybeeta so \progressetaright fires and
$E_x$ is unified with $\lambda y.y$, resulting in
$\sigma = \{~ A \mapsto \lambda x.\lambda y.x ~;~ B_x \mapsto \lambda y.x ~;~ C_{yx} \mapsto x ~;~ E_x \mapsto \lambda y.y~\}$.\\
The remaining simplify step $\hoUnifPb_2$ identified $D$ with $F$,
hence the resulting \Fo{} substitution is
$\rho = \{X \mapsto \lambda x.\lambda y.y ~;~ Y \mapsto \lambda x.(f\appsep (\lambda y.y))\appsep x\}$.
\todo{verificare, la vecchia soluzione era sballata}

>>>>

\noindent
The resolution of $\hoUnifPb_1$ assigns $\lambda x.\lambda y.x$ to $A$
that in turn triggers $\linkStore_3$ and then $\linkStore_4$ by \progressetaleft,
one per $\lambda$ in the solution of $A$.
The unification variable $C_{yx}$ is therefore unified with $x$
(the second variable of its scope).
As a result $\linkStore_1$ becomes \linketaM{x}{E_x}{\lambda y.y},
and the \rhs is no more in \maybeeta so \progressetaright fires and
$E_x$ is unified with $\lambda y.y$, resulting in
$\sigma = \{~ A \mapsto \lambda x.\lambda y.x ~;~ B_x \mapsto \lambda y.x ~;~ C_{yx} \mapsto x ~;~ E_x \mapsto \lambda y.y~\}$.\\
The remaining simplify step $\hoUnifPb_2$ identified $D$ with $F$,
hence the resulting \Fo{} substitution is
\todo{verificare, la vecchia soluzione era sballata}
$\rho = \{X \mapsto \lambda x.\lambda y.y ~;~ Y \mapsto \lambda x.(f\appsep (\lambda y.y))\appsep x\}$.
